Cover Letter

### 2021-09-20 paper/latex/NetworkNeuroscience/cover_letter.tex
update letter

\documentclass[NETN,manuscript]{stjour-new}
\articletype{Research}
\usepackage{graphicx}
\graphicspath{ {figs/} }
\usepackage{hyperref}
% \input{preamble.tex}
% \usepackage[utf8]{inputenc}
% \usepackage{geometry}
% \usepackage{amsmath}
% \usepackage{graphicx}
% \usepackage[style=apa]{biblatex}
% \usepackage{natbib}
% \usepackage[font=footnotesize,labelfont=bf]{caption}
% \addbibresource{rmt.bib}
% \bibliographystyle{plain}
% \bibliography{rmt}
\begin{document}

\title{Cover Letter}
\date{\today}

\author[Derek Berger, Gurpreet Matharoo, Jacob Levman]{
    Derek M. Berger\affil{1},
    Gurpreet S. Matharoo\affil{2}
    \and Jacob Levman\affil{3}
}
\affiliation{1}{Computer Science, St. Francis Xavier University, Antigonish, Canada, dberger@stfx.ca}
\affiliation{2}{Physics, St. Francis Xavier University, Antigonish, Canada, gmatharo@stfx.ca}
\affiliation{3}{Computer Science, St. Francis Xavier University, Antigonish, Canada, jlevman@stfx.ca}

@@

To the Editors of Network Neuroscience

We believe our manuscript \emph{Random Matrix Theory Tools for the Analysis of Functional Magnetic
Resonance Imaging Examinations} would be an excellent fit for Network Neuroscience as a
\emph{Research} article. Our use of random matrix theory (RMT) for the analysis of functional
connectivity in functional magnetic resonance imaging (fMRI) falls clearly within the \href{https://direct.mit.edu/netn/pages/submission-guidelines#aims}{Aims and Scope}
of \emph{Network Neuroscience}.

@@

Should you consider to review our manuscript, we believe the following reviewers would be suitable:

@@

All authors approve the manuscript in its submitted form, and have no conflicts of interest,
financial or otherwise. [Names, affiliations, email addresses and funding information]

\textbf{[1]} A poster of some preliminary results of our study was presented at the ISMRM annual
conference \citep{bergerOpenSourceRandom2021}.

Sincerely, \\
Corresponding Author \\
Institution Title \\
Institution/Affiliation Name \\
Institution Address \\
Corresponding author e-mail address \\

~\\
\textbf{Additional Contact} [should the corresponding author be unavailable] \\
Institution Title \\
Institution/Affiliation Name \\
Institution Address \\
e-mail address \\

\bibliography{rmt}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{url}
% \usepackage{apalike}
% \documentclass[NETN,manuscript]{stjour-new}
% \articletype{Research}
\usepackage{graphicx}
\graphicspath{ {figs/} }
% \input{preamble.tex}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
% \usepackage[backend=biber,
%             style=authoryear,
%             natbib=true,
% ]{biblatex}
% \addbibresource{cover.bib}
\usepackage{fancyhdr}
% \usepackage{natbib}
% \usepackage[font=footnotesize,labelfont=bf]{caption}
% \addbibresource{rmt.bib}
% \bibliographystyle{plain}
% \bibstyle{plain}
% \bibliography{cover_letter}

\begin{document}
\bibliographystyle{plain}
\thispagestyle{fancy}
% \addtolength{\topmargin}{-63.87003pt}
\fancyhead[C]{\includegraphics[height=0.5in]{stfx_text.png}}
\fancyhead[L]{\includegraphics[height=0.5in]{crest.png}}
\fancyhead[R]{
    \sffamily
    \scriptsize
    4130 University Avenue \\
    B2G 2W5 \\
    Antigonish, Nova Scotia \\
    Canada
}
\normalsize

\title{Cover Letter}
% \begin{center}
% \includegraphics[width=4in]{stfx_logo.png}
% \end{center}

% \author[Derek Berger, Gurpreet Matharoo, Jacob Levman]{
%     Derek M. Berger\affil{1},
%     Gurpreet S. Matharoo\affil{2}
%     \and Jacob Levman\affil{3}
% }
% \affiliation{1}{Computer Science, St. Francis Xavier University, Antigonish, Canada, dberger@stfx.ca}
% \affiliation{2}{Physics, St. Francis Xavier University, Antigonish, Canada, gmatharo@stfx.ca}
% \affiliation{3}{Computer Science, St. Francis Xavier University, Antigonish, Canada, jlevman@stfx.ca}

@@

~\\~\\
To the Editors of Network Neuroscience, \\

We hope you will consider our manuscript \emph{Random Matrix Theory Tools for the Analysis of
Functional Magnetic Resonance Imaging Examinations} for publication in Network Neuroscience as a
\emph{Research} article.

In our manuscript, we apply some of the analytical and statistical tools of random matrix theory
(RMT) to analyze a wide variety of fMRI data in a predictive framework, and release open-source
software to facilitate such analyses with a wide variety of data.

Our use of random matrix theory (RMT) for the analysis of functional
connectivity in functional magnetic resonance imaging (fMRI) falls clearly within the
\href{https://direct.mit.edu/netn/pages/submission-guidelines#aims}{Aims and Scope} of \emph{Network
Neuroscience}.

@@

This paper is not under consideration at any other journal, although a poster of some preliminary
results of our study was presented at the International Symposium for Magnetic Resonance in Medicine
2021 annual conference \citep{bergerOpenSourceRandom2021}. Our lab has REB ethics approval for
conducting retrospective analyses, although we are unaware of the need for this, this being an
analysis of anonymized public data. All authors approve the manuscript in its submitted form, and
have no conflicts of interest, financial or otherwise.

Should you consider to review our manuscript, we believe the following reviewers would be suitable
due to expertise in this areas of research:

@@

Sincerely,\\ \textbf{Corresponding Author}\\
Jacob Levman, PhD (jlevman@stfx.ca) \\
Canada Research Chair in Bioinformatics \\
Department of Computer Science \\
St. Francis Xavier University

\textbf{Additional Contacts} [should the corresponding author be unavailable]\\
Derek Berger (dberger@stfx.ca), Department of Computer Science, St. Francis Xavier University\\
Gurpreet S. Matharoo (gmatharo@stfx.ca), Department of Physics, St. Francis Xavier University

\today{}

[Names, affiliations, email addresses and funding information]

% \printbibliography % biblatex
\bibliography{cover.bib}  % natbib
